Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-04-10 tex/MesnardoBarba2019.tex
Revise user-experience paragraphs

% Mention the 7-day limitation for jobs with Azure Batch. (WARNING: according to the Batch Shipyard documentation, tasks can have a maximum lifetime of 180 days.)
% Mention that Batch Shipyard can pull images from public and private registries.
% Mention that Singularity containers are also supported in Batch Shipyard.

@@

Command-line tools such as Azure-CLI and Batch Shipyard were greatly helpful to create and submit everything from our local terminal. (In our research lab, we tend to avoid, as much as possible, interacting with graphical-user interfaces, to make our workflow more reproducible.)
Azure-CLI helped us to setup the Azure Batch account and its associated Azure Storage, as well as uploading/downloading simulation data.
With Batch Shipyard, we did not need to have experience with the software development kit to use Azure Batch.
We have used Batch Shipyard to submit jobs on Azure Batch to run Docker container-based multi-instance tasks.
Note that Batch Shipyard also support Singularity containers.

Our in-house CFD research software makes use of the MPI library to run applications on distributed-memory architectures.
We used Azure instances that feature a network interface for remote direct memory access (RDMA) connectivity, allowing nodes in the same pool to communicate over an InfiniBand network.
As of this writing, only Intel MPI 5.x versions are supported with the Azure Linux RDMA drivers.

Moreover, Microsoft Azure implements quotas, such as the maximum number of cores that can be used in a certain region.
To run our simulations, we had to open online customer support requests every time we wanted to increase our core quota for a subscription, with a certain service in certain region with a certain type of instances.
We had to go through this process at least five times during our sponsorship period.

>>>>

@@

Command-line utilities such as Azure-CLI and Batch Shipyard were greatly helpful to create and manage resources on Microsoft Azure to conduct reproducible research.
(In our lab, we tend to avoid interacting directly with graphical-user interfaces to keep a trace of the commands run and make the workflow more reproducible.)
Azure-CLI helped us setup the Azure Batch and Storage accounts as well as moving data between the cloud platform and our local machines.
Thanks to Batch Shipyard, we did not have to dig into the software development kit of Azure Batch to use the service.
Writing YAML configuration files was all we needed to create a pool of virtual machines with Batch Shipyard and to submit jobs to it.
With Batch Shipyard, we have painlessly submitted jobs on Azure Batch to run multi-instance tasks in Docker containers; everything from the command-line terminal on a local machine.
Note that Bach Shipyard also support Singularity containers.

Our in-house CFD software, PetIBM, relies on MPI to run applications on distributed-memory architectures.
The Poisson system is solved on distribute GPU devices using the NVIDIA AmgX library.
Thus, we have used Azure instances of the NC-series that feature a network interface for remote direct memory access (RDMA) connectivity, allowing nodes in the same pool to communicate over InfiniBand network.
As of this writing, only Intel MPI 5.x versions are supported with the Azure Linux RDMA drivers.

Moreover, Microsoft Azure implements quotas and limits on resources with Azure Batch service, such as the maximum number of dedicated cores that can used in a certain region.
To be able to run our simulations, we had to contact Azure Support through Azure Portal to request a quota increase for a given type of instances in a specific region and for a given subscription.
We had to go through this process at least five times during our sponsorship period.
The readers should be aware of these quotas and limits before scaling up workloads on Azure Batch.
